Species motif participation provides unique information about species risk of extinction

### 2023-04-27 manuscript/reorder_main_text.tex

    \begin{figure}[ht!]
        \centering
        \includegraphics[width=0.9\textwidth]{figures/persistence_vs_SC_lm.eps}
        \caption{\textbf{A,C} Mean persistence of consumers in a network decreased strongly with increasing probability of disturbance to basal resources and decreased slightly, but significantly, with increasing connectance. There was no significant relationship between mean persistence and network size.
        \textbf{B} Persistence of consumers increased with increasing in-degree when the probability of extinction for basal resources was low but decreased with increasing in-degree when the probability of extinction was high.
        \textbf{D} Persistence of consumers decreased with increasing STL at all levels of disturbance.}
        \label{fig:lm_CS}
    \end{figure}

@@

    \begin{figure}[hb!]
        \centering
        \includegraphics[width=\textwidth]{figures/persistence_motif_profiles.eps}
        \caption{The proportions of the four motifs in a network's motif profile are related to the mean persistence of species in the network. Specifically, persistence decreases as the proportion of omnivory in the network's motif profile increases while persistence increases with the proportion of the apparent competition motifs. Interactions between motif profiles and disturbance were not significant. Here we show the relationships of probabilities of extinction of basal resources of $\pi=0.1$ (top set of lines) and $\pi=0.5$ (bottom set of lines). Relationships are shown for the observed range of proportions for each motif.}      
        \label{fig:motif_profile_persistence}
    \end{figure}

>>>>

    \begin{figure}[ht!]
        \centering
        \includegraphics[width=\textwidth]{figures/persistence_vs_SC_lm.eps}
        \caption{
        \textbf{A} Persistence of consumers increased with increasing in-degree when the probability of extinction for basal resources was low but decreased with increasing in-degree when the probability of extinction was high.
        \textbf{B,E} Mean persistence of consumers in a network decreased strongly with increasing probability of disturbance to basal resources and decreased slightly, but significantly, with increasing connectance. There was no significant relationship between mean persistence and network size.
        \textbf{C} Mean persistence of consumers decreased with increasing proportions of omnivory in the network's motif profile and increased with increasing proportions of other motifs. Persistence also decreased significantly with increasing probability of basal species extinction but there was no significant interaction; we therefore show trends only for $\pi$=0.1.
        \textbf{D} Persistence of consumers decreased with increasing STL at all levels of disturbance.}
        \label{fig:lm_CS}
    \end{figure}

@@

    % \begin{figure}[hb!]
    %     \centering
    %     \includegraphics[width=\textwidth]{figures/persistence_motif_profiles.eps}
    %     \caption{The proportions of the four motifs in a network's motif profile are related to the mean persistence of species in the network. Specifically, persistence decreases as the proportion of omnivory in the network's motif profile increases while persistence increases with the proportion of the apparent competition motifs. Interactions between motif profiles and disturbance were not significant. Here we show the relationships of probabilities of extinction of basal resources of $\pi=0.1$ (top set of lines) and $\pi=0.5$ (bottom set of lines). Relationships are shown for the observed range of proportions for each motif.}      
    %     \label{fig:motif_profile_persistence}
    % \end{figure}
